---
title: "Covid-19: Asian X Factor"
output:
  pdf_document: default
  html_document: default
---

## Purpose of Thie Report
In my country (an Asian country), it has been rumored that the Asians have a factor preventing the fatality of COVID-19, which is called "Factor X". In this report, I'll show whether the Asians have "Factor X" and the lower number of deaths than others.

Conclusion: there is no obvious "Factor X".

## Importing Libraries
Importing packages for this project.

You have to manually install the package below before run.
```
install.packages("tidyverse")
install.packages("lubridate")
```

```{r import_packages, message=FALSE}
library(tidyverse)
library(lubridate)
```

## Loading Data
This section is to load the data of COVID-19 from the GitHub repository of the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University. Most of the data sources are from the official institute in each country.

```{r import_data, message=FALSE}
url_in <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/"
file_names <- c(
  "time_series_covid19_confirmed_global.csv",
  "time_series_covid19_deaths_global.csv"
)
urls <- str_c(url_in, file_names)

global_cases <- read_csv(urls[1])
global_deaths <- read.csv(urls[2])
```

## Importing and Modifying Data
Here, I tidy and transform the data: joining case, deaths and population together.
```{r tidy_transform, message=FALSE}
tidy_global_deaths <- global_deaths %>%
  pivot_longer(cols = -c(`Province.State`, `Country.Region`, Lat, Long),
               names_to = "date",
               values_to = "deaths") %>%
  rename(Country_Region = `Country.Region`) %>%
  mutate(date = mdy(str_replace(date, pattern="X", replacement=""))) %>%
  select(-c(Lat, Long)) %>%
  group_by(Country_Region, date) %>%
  summarise(deaths = sum(deaths))

tidy_global_cases <- global_cases %>%
  pivot_longer(cols = -c(`Province/State`, `Country/Region`, Lat, Long),
               names_to = "date",
               values_to = "cases") %>%
  rename(Country_Region = `Country/Region`) %>%
  mutate(date = mdy(date)) %>%
  select(-c(Lat, Long)) %>%
  group_by(Country_Region, date) %>%
  summarise(cases = sum(cases))

global <- tidy_global_cases %>%
  full_join(tidy_global_deaths, by = c("date" = "date","Country_Region" = "Country_Region"))

global
```
And this is the summary of joined data.
```{r summary_data, message=TRUE}
summary(global)
```

## Visualizing Data
### The Number of Global Cases and Deaths in the Logarithmic Scale
I summed up the number of cases and deaths by date, and showed it as the graph below.
```{r group_by_date}
global_by_date <- global %>%
  group_by(date) %>%
  summarise_each(funs(sum),
                 vars = c(cases = cases, deaths = deaths))

global_by_date %>%
  filter(vars...cases > 0) %>%
  ggplot(aes(x = date, y = vars...cases)) +
  geom_line(aes(color = "vars...cases")) +
  geom_point(aes(color = "vars...cases")) +
  geom_line(aes(y = vars...deaths, color = "vars...deaths")) +
  geom_point(aes(y = vars...deaths, color = "vars...deaths")) +
  scale_y_log10() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90)) +
  labs(title = "Global COVID19", y = NULL)
```
### The Proportion of Deaths by Cases in Each Country
I plotted the deaths by cases in the log scale.

```{r deathes_by_cases}
latest_date <- global %>%
  filter(cases > 0) %>%
  group_by(Country_Region) %>%
  filter(date == max(date)) %>%
  ungroup()
latest_date %>%
  ggplot(aes(x = cases, y = deaths, label = Country_Region)) +
  geom_point(aes(color = "")) +
  scale_y_log10() +
  scale_x_log10() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90)) +
  labs(title = "Global COVID19")
```

### Modeling (cases vs deaths)
I created a model of cases vs deaths. The model looks so good that it is clear that there is no obvious "Factor X". If there were, the dots look more scattered.

```{r modeling}
mod <- lm(deaths ~ cases, data = latest_date)
summary(mod)
```

```{r prediction}
latest_date_w_pred <- latest_date %>%
  mutate(pred = predict(mod))

latest_date_w_pred %>%
  ggplot(aes(cases, deaths)) +
  geom_point(color = "red") +
  stat_smooth(method = lm) +
  scale_y_log10() +
  scale_x_log10()
```

### Possible Bias
But there might be two biases:
1. the reported number is more likely to be missing if there is more cases and deaths because of insufficient capacity of collecting data
2. each country uses its own standard of counting, which leads to an unriliable result